\LARGE \bf Approximately Orchestrated Road Traffic Automata\\ a General Traffic Simulation Framework

### 2012-03-13 papers/itsc_2012/final.tex
added a bunch of comments to section III and IV

\commentd{consider re-grouping sections... maybe this is all 'methodology'?}

@@

AORTA's implementation uses Scala, a language implemented on the Java Virtual
Machine. Scala provides the advantage of functional programming constructs while
still permitting imperative style. Parts of AORTA, including extensions and
clients, can easily be written in Java or Scala. The software is
open-source\footnote{http://code.google.com/p/road-rage} and easily extensible.
The stop sign policy used in Section \ref{sec:results}'s experiments is
implemented in just $70$ lines of code.

@@

One advantage of AORTA is that it simulates traffic on existing infrastructure
rather than contrived, randomly generated maps. Utilizing OpenStreetMaps, a
community project offering user-editable, free XML-based maps, enables this. To
run a simulation on a map from OSM, there is a one-time conversion process to
transform the map into AORTA's format, which is also encoded with XML.

@@

The map also has a geometric interpretation, used for visualization and physical
distances. A road contains a sequence of points giving the line segments of the
center yellow line. These points could also be interpreted as control points for
a curved road, but AORTA uses straight lines as an approximation. Lanes are
parallel to the center line, some fixed width apart from one another. Turns are
modeled with a single straight line connecting the end of one lane to the start
of another (so right turns often have $0$ length).

@@

Map construction is split into several passes, each feeding the next.
\begin{enumerate}
  \item OSM encodes many paths besides driveable roads, so the builder first filters
        these out. Next the builder marks GPS locations common to multiple roads, since
        they implicitly indicate intersections.
  \item OSM \emph{ways} (sequences of GPS locations) include many
        intersections, so the builder next splits ways into undirected
        segments of roads between exactly two intersections.
  \item The builder multiplies undirected roads into directed lanes in each direction
        (unless the road is marked one-way). The builder guesses the number of lanes based on
        OSM's ``road type'' tag or an explicit number of lanes, when that data is available.
  \item The builder constructs turns between incoming and outgoing lanes at each
        junction. The builder uses an angle heuristic to choose between left, right, straight,
        and U-turns. When several lanes all cross into fewer lanes,
        the builder forces merging of the rightmost lanes.  Although inaccurate,
        these patterns are the best compromise. At the time of writing, even sources
        like Google Maps \cite{googleMaps} lack this information.
  \item Because turns are heuristically placed, the graph is often
        disconnected. In order to ensure that an agent will be able to reach any point in the map,
        the builder removes all but the largest strongly connected component of the digraph.
        Disconnected lanes are spliced out of larger roads, leaving unappealing
        geometric gaps, but correctly ensuring connectivity for corner-case free
        pathfinding.
  \item The builder serializes the graph in a simple XML format.
\end{enumerate}

>>>>

\commentd{consider re-grouping sections... maybe this is all 'methodology'?} \commentpk{I think it is fine as it is}

@@

AORTA's implementation uses Scala, a language implemented on the Java Virtual
Machine \commentpk{cite a link to Scala here}. Scala provides the advantage of
functional programming constructs while still permitting imperative style.
Parts of AORTA, including extensions and clients, can easily be written in Java
or Scala. The software is
open-source\footnote{http://code.google.com/p/road-rage} and easily extensible
\commentpk{maybe "Extensions and clients built on top of AORTA can be written
in either Java or Scala, as the software is
open-source\footnote{\commentpk{needs more description}
http://code.google.com/p/road-rage} and easily extensible}. \commentpk {For
instance, the} The stop sign policy used in Section \ref{sec:results}'s
experiments \commentpk{Sec VI's experiments is awk, maybe "used in experiments
described in Sec VI"} is implemented in just $70$ \commentpk{remove \$\$ in
latex code, here and elsewhere} lines of code.

\commentpk{need to reference the architecture figure here. the text in the
figure also needs to be bigger}

@@

One advantage of AORTA is that it simulates traffic on existing infrastructure
rather than contrived, randomly \commentpk{"contrived, randomly" is a bit
weird, maybe "contrived or randomly"?} generated maps. Utilizing OpenStreetMaps
\commentpk{remove trailing s in OpenStreetMaps}, a community project offering
user-editable, free XML-based maps, enables this. To run a simulation on a map
from OSM, there is a one-time conversion process to transform the map into
AORTA's format, which is also encoded with XML. \commentpk{why convert it to
another XML format? you might want to put an additional line outlining the
purpose of this step}

@@

The map also has a geometric interpretation, used for visualization and
\commentpk{measuring?} physical distances. A road contains a sequence of points
giving the line segments of the center yellow line \commentpk{if you want to
use "yellow", you need to reference a figure. I would recommend putting it this
way "center line of the road (yellow lines in Fig. XX)"}. These points could
also be interpreted as control points for a curved road, but AORTA uses
straight lines as an approximation. Lanes are parallel to the center line, some
fixed width apart from one another \commentpk{no need to mention that the roads
could be interpreted as a spline, instead say "AORTA interprets roads as
straight lines between these points, and projects parallel lanes out using a
fixed width"}. Turns are modeled with a single straight line connecting the end
of one lane to the start of another (so right turns often have $0$ length).

@@

Map construction is split into several passes, each feeding the next.
\begin{enumerate}
  \item OSM encodes many paths besides driveable roads, so the builder first filters
        these out. Next the builder \commentpk{you have not mentioned a builder before, maybe mention it in the last line of the intro to this section} marks GPS locations common to multiple roads, since
        they implicitly indicate intersections \commentpk{do you guys use GPS locations or OSM unique identifiers, what about overpasses etc.?}.
  \item OSM \emph{ways} (sequences of GPS locations) include many
        intersections, so the builder next splits ways into undirected
        segments of roads between exactly two intersections.
  \item The builder multiplies undirected roads into directed lanes in each direction
        (unless the road is marked one-way). The builder guesses the number of lanes based on
        OSM's ``road type'' \commentpk{If you have space, elaborate that you use heuristics on the road type attribute, and the 4 different road types are residential etc.} tag or an explicit number of lanes, when that data is available.
  \item The builder constructs turns between incoming and outgoing lanes at each
        junction \commentpk{intersection, keep the terminology constant}. The builder uses an angle heuristic to choose between left, right, straight,
        and U-turns \commentpk{preceding sentence unclear to me}. When several lanes all cross into fewer lanes,
        the builder forces merging of the rightmost lanes.  Although inaccurate,
        these patterns are the best compromise. At the time of writing, even sources
        like Google Maps \cite{googleMaps} lack this information \commentpk{the last sentence is tricky. unless you have a source that states this, I would avoid this claim. Linking to google maps directly is not correct}.
  \item Because turns are heuristically placed, the graph is often
        disconnected. In order to ensure that an agent will be able to reach any point in the map,
        the builder removes all but the largest strongly connected component of the digraph.
        Disconnected lanes are spliced out of larger roads, leaving unappealing
        geometric gaps, but correctly ensuring connectivity for corner-case free
        pathfinding.
  \item The builder serializes the graph in a simple XML format.
\end{enumerate}
